Real-space computation of $E$/$B$-mode maps I: Formalism, Compact Kernels, and Polarized Filaments

### 2018-07-23 articles/formalism/sections/real_space_formalism.tex
Fix small typo in 3.3.

The kernel $\mathcal{M}_G$ is the Green's function of the operator that transforms Stoke parameters to coordinate independent $E/B$.  The coordinate independence implies that the real and imaginary parts of the kernel do not vary with changes in the galactic latitude and longitude of the central pixel. In particular these functions are not distorted when a part of the domain overlaps with the poles, as can be seen in the first two rows of \fig{fig:vis_kernel}. From \eq{eq:qu2eb_radiation_concise}, we can see the $E/B$ patterns that Kronecker $\delta$-functions in the Stokes parameter pixels produce:
%
\beq
\bmat E= \textrm{Re}(\mathcal{M}_G) \\ B =\textrm{Im}(\mathcal{M}_G)  \emat  \leftarrow \bmat Q=\frac{\delta(\hat{n} - \hat{n}_q)}{\Delta \Omega}\\ U=0 \emat ;\qquad
\bmat E= -\textrm{Im}(\mathcal{M}_G) \\ B = + \textrm{Re}(\mathcal{M}_G)  \emat  \leftarrow \bmat Q=0 \\ U=\frac{\delta(\hat{n} - \hat{n}_q)}{\Delta \Omega} \emat.
\eeq
%
On the other hand, $\mathcal{M}^*_B$ is the Green's function of the operator that transforms $E/B$ to coordinate-dependent Stokes parameters $Q/U$.   The kernel $\mathcal{M}^*_B$ does not change with the central longitude, but varies as a function of galactic latitude. This latitude-dependent shape carries the  coordinate dependence of the Stokes parameters. From \eq{eq:eb2qu_radiation}, we $\mathcal{M}^*_B$ arises from $\delta$-functions in $E/B$:
%
\beq
\bmat Q= \textrm{Re}(\mathcal{M}^*_B) \\ U = \textrm{Im}(\mathcal{M}^*_B)  \emat  \leftarrow \bmat E=\frac{\delta(\hat{n} - \hat{n}_e)}{\Delta \Omega}\\ B=0 \emat;\qquad
\bmat Q= -\textrm{Im}(\mathcal{M}^*_B) \\ U = +\textrm{Re}(\mathcal{M}^*_B)  \emat  \leftarrow \bmat E=0 \\ B=\frac{\delta(\hat{n} - \hat{n}_e)}{\Delta \Omega} \emat\,.
\eeq
%
Recall that the complex conjugates of these functions switch roles to form the convolution kernels (For example, $\mathcal{M}_G^*$ is the convolution kernel for $E/B \rightarrow Q/U$.).  It is also interesting to note that the radiation kernel ($\mm_{G}$) and the convolution kernel ($\mm_{B}$) become progressively identical as one approaches the equator as seen in  \fig{fig:vis_kernel}, which is a consequence of $\gamma \simeq -\alpha$ in the vicinity of the equator. The equator is the place on the sphere most akin to the flat sky case, where the radiation and convolution kernels are expected to be identical.

>>>>

The kernel $\mathcal{M}_G$ is the Green's function of the operator that transforms Stoke parameters to coordinate independent $E/B$.  The coordinate independence implies that the real and imaginary parts of the kernel do not vary with changes in the galactic latitude and longitude of the central pixel. In particular these functions are not distorted when a part of the domain overlaps with the poles, as can be seen in the first two rows of \fig{fig:vis_kernel}. From \eq{eq:qu2eb_radiation_concise}, we can see the $E/B$ patterns that Kronecker $\delta$-functions in the Stokes parameter pixels produce:
%
\beq
\bmat E= \textrm{Re}(\mathcal{M}_G) \\ B =\textrm{Im}(\mathcal{M}_G)  \emat  \leftarrow \bmat Q=\frac{\delta(\hat{n} - \hat{n}_q)}{\Delta \Omega}\\ U=0 \emat ;\qquad
\bmat E= -\textrm{Im}(\mathcal{M}_G) \\ B = + \textrm{Re}(\mathcal{M}_G)  \emat  \leftarrow \bmat Q=0 \\ U=\frac{\delta(\hat{n} - \hat{n}_q)}{\Delta \Omega} \emat.
\eeq
%
On the other hand, $\mathcal{M}^*_B$ is the Green's function of the operator that transforms $E/B$ to coordinate-dependent Stokes parameters $Q/U$.   The kernel $\mathcal{M}^*_B$ does not change with the central longitude, but varies as a function of galactic latitude. This latitude-dependent shape carries the  coordinate dependence of the Stokes parameters. From \eq{eq:eb2qu_radiation}, we $\mathcal{M}^*_B$ arises from $\delta$-functions in $E/B$:
%
\beq
\bmat Q= \textrm{Re}(\mathcal{M}^*_B) \\ U = \textrm{Im}(\mathcal{M}^*_B)  \emat  \leftarrow \bmat E=\frac{\delta(\hat{n} - \hat{n}_e)}{\Delta \Omega}\\ B=0 \emat;\qquad
\bmat Q= -\textrm{Im}(\mathcal{M}^*_B) \\ U = +\textrm{Re}(\mathcal{M}^*_B)  \emat  \leftarrow \bmat E=0 \\ B=\frac{\delta(\hat{n} - \hat{n}_e)}{\Delta \Omega} \emat\,.
\eeq
%
Recall that the complex conjugates of these functions switch roles to form the convolution kernels. (For example, $\mathcal{M}_G^*$ is the convolution kernel for $E/B \rightarrow Q/U$.)  It is also interesting to note that the radiation kernel ($\mm_{G}$) and the convolution kernel ($\mm_{B}$) become progressively identical as one approaches the equator as seen in  \fig{fig:vis_kernel}, which is a consequence of $\gamma \simeq -\alpha$ in the vicinity of the equator. The equator is the place on the sphere most akin to the flat sky case, where the radiation and convolution kernels are expected to be identical.
